### 2012-12-03 inst/examples/policycosts/policycosts_writeup_c0_30.Rmd
run on zero

`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="policycost-cache/" or`

``` {r libraries, include=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"))
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

```{r setup}
seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 100              # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- 0.2              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
profit <- profit_harvest(price = 10, c0 = 0, c1 = 0)
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
````

```{r reed, dependson="setup"}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)
````

``` {r fees}
L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
none <- function(h, h_prev)  0
penaltyfns <- list(L2=L2, L1=L1, free_decrease=free_decrease, fixed=fixed, free_increase=free_increase)
c2 <- seq(0, 10, length.out = 30)
````

## Apples to Apples levels

This can take a while, so we use explicit parallelization, 
``` {r  parallel}
require(snowfall)
sfInit(cpu=8, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

## Loop over penalty functions and magnitudes

``` {r  bigloop, dependson=c("setup", "reed", "fees")}
policies <- 
sfSapply(penaltyfns, function(penalty){
  policies <- 
  sapply(c2, function(c2){
      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = penalty(c2))
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) 
  })
})
````

Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.  This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.

Quadratic costs on fishing effort have to be done separately,

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) .1*c2*h/x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````

Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.

``` {r npv-plot, dependson="quadcosts"}
npv0 <- dat[1,3] 
npv0
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:

```{r apples_plot, dependson="quadcosts"}
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

```{r apples, dependson="quadcosts"}
closest <- function(x, v){
  which.min(abs(v-x))
}
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/value), by=variable]
apples <- c2[index$V1]
names(apples) = index$variable
apples
````

>>>>

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="policycosts-cache-c0-30/")
```

```{r}
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
c2 <- seq(0, 20, length.out = 40)
```

```{r run, results="hide"}
knit("policycosts.Rmd", "policycosts_c0_30.md")
```
